\input{settings} % add packages, settings, and declarations in settings.tex
\usepackage{url}
\usepackage{amsmath,amssymb,amsthm}


\newcommand{\Prob}[1]{{{\bf{Pr}}\left[{#1}\right]}}
\newcommand{\Mean}[1]{{\mathbb E}\left[{#1}\right]}
\newcommand{\Var}[1]{{\mathbb Var}\left[{#1}\right]}


\begin{document}

\lhead{Prof. C.E. Tsourakakis} 
\rhead{CS365 Spring '23 \\ Foundations of Data Science \\ Assignment 2} 
\cfoot{\thepage\ of \pageref{LastPage}}


\section*{Instructions}
\framebox{%
	\begin{minipage}{0.9\linewidth}
		\begin{itemize}
			\item The homework is due on \underline{{\bf Friday 2/10 at 5pm ET}}.  
			\item No extension will be provided, unless for serious documented reasons.
			\item {\bf Start early!}
			\item Study the material taught in class, and feel free to do so in small groups, but the solutions should be a product of your own work. 
			\item This  is not a multiple choice homework;   reasoning, and mathematical proofs are required before giving your final answer.
			\item The code necessary for problem 2 should be written in the Jupyter notebook handed out to you. 
		\end{itemize}
\end{minipage}}

\section{Probability [25 points]}   

Solve the following problems:
\begin{itemize}
	\item[a.] (5pts)  Let $X,Y$ be independent random  variables with common density function $f$. Prove that the density function of $Z=\max(X,Y)$ is given by 
 $f_Z(x)=2f(x)\mathbb{P}(X \leq x)$.
 \item[b.]  (10pts) If $U$ is a uniform random variable in $[0,1]$, what is the distribution of $\lfloor 100 U \rfloor +1$? 
	\item[c.] (10pts)  If $U$ is a uniform random variable in $[0,1]$ and $0<q<1$, prove that $X=1+   \lfloor \frac{\log U}{\log q} \rfloor$ has a geometric distribution. What is the parameter of the geometric distribution? 
\end{itemize}

 
\section{Bayes rule [20 points]}   

Let $N$ be a discrete random variable that takes values from the set $\{1,n\}$ with equal probability, i.e., $\Prob{N=1}=\Prob{N=n}=\frac{1}{2}$. Consider the following process. 

\begin{itemize}
	\item First we draw a value for $N$.
	\item Then, we draw $N$ iid uniform RV $\{X_i\}_{i=1,\ldots,N}$ in $[0,1]$.
\end{itemize}

Someone tells you the value $Z=\min_{i=1,\ldots,N} X_i = 0.05$, namely the smallest value among the $N$ uniform RVs drawn. However you do not know the value of $N$.  

 

\begin{tcolorbox}
	What is the probability $\Prob{N=1|Z=0.05}$ when: (a) $n=2$, and (b) $n=10$. 
 \end{tcolorbox}



\section{Needles and Probability [55 Points] }  

 The Jupyter notebook in on Git.
 

\end{document}
